\documentclass{leadsheet}
\input{../include/env}

\begin{document}
\setleadsheets{
  align-chords={l} 
  , verse/template=toplabel
  , chorus/template=toplabel
  , chorus/label-format={\textbf}
  , interlude/template=toplabel
  , interlude/label-format={\textbf}
   ,print-chords=false
}
\setsbfontsize{14pt}

\begin{song}[verse/numbered,remember-chords]
  { , title={Red is the Rose}
    , key=D
  }
  \begin{multicols}{2}
    \begin{verse}
      Come ^{D}over the hills, \\
      my ^{Em}bonnie Irish lass.^{A} \\
      Come ^{D}over the ^{D/B}hills 
      to your ^*{G}dar ^{A}ling. \\
      ^{G}You choose the ^{D}road, love, \\
      and ^{Em}I'll make the ^{A}vow. \\
      And ^{D}I'll be your ^{G}true love \\ 
      for^*{A}e - ^{D}ver. \\
    \end{verse}

    \begin{chorus}[format={\itshape}]
      ^{D}Red is the rose \\
      that in ^{Em}yonder garden grows,^{A} \\
      ^{D}fair is the ^{D/B}lily of the ^*{G}val ^{A}ley, \\
      ^{G}clear is the ^{D}water \\
      that ^{Em}flows from the ^{A}Boyne, \\
      but ^{D}my love is ^{G}fairer than ^*{A}a - ^{D}ny. \\
    \end{chorus}
    \columnbreak

    \begin{verse}
      'Twas ^down by Killarney's \\
       green ^woods that we strayed^. \\
      When the ^moon and the ^stars \\
      they were ^*shi ^ning. \\
      The ^moon shone its ^rays \\
      on her ^locks of golden ^hair, \\
      And she ^swore she'd be ^my love \\
      for^*e - ^ver. \\
    \end{verse}
  
    \begin{chorus}[after-label=]\end{chorus}

    % \columnbreak

    \begin{verse} 
      It's ^not for the parting  \\
      ^that my sister pains^. \\
      It's ^not for the ^grief of my ^*mo ^ther. \\
      'Tis ^all for the ^loss of my ^bonny \\ Irish ^lass, \\
      that ^my heart is ^breaking for^*e - ^ver. \\
    \end{verse}

    \begin{chorus}[after-label=]\end{chorus}

  \end{multicols}
\end{song}
\end{document}




  


 