\documentclass{leadsheet}
\input{../include/env}

\begin{document}
\setleadsheets{
  align-chords={l} 
  , verse/template=toplabel
  , chorus/template=toplabel
  , chorus/label-format={\textbf}
  , interlude/template=toplabel
  , interlude/label-format={\textbf}
  %,print-chords=false
}
\setsbfontsize{14pt}

\begin{song}[verse/numbered,remember-chords]
  { , title={Will the circle be unbroken}
    , key=G
    , composer={Jonny Cash, arr. Reinhard Simmgen}
    , lyrics={Jerry Lee Lewis}
  }
  \begin{multicols}{2}

    \begin{chorus}[format={\itshape}]
      Will the ^{G}circle be unbroken, \\
      by and ^{C}by Lord, by and ^{G}by. \\
      There's a better home a^{Em}waiting, \\
      in the ^{G}sky Lord, ^{D}in the ^{G}sky. \\
    \end{chorus}

    \begin{verse}
      I was ^{G}standing by the window, \\
      on one ^{C}cold and cloudy ^{G}day. \\
      When I saw the hearse come ^{Em}rolling, \\
      for to ^{G}carry my ^{D}mother a^{G}way. \\
    \end{verse}

    \begin{chorus}[after-label=]\end{chorus}

    \begin{verse}
      I said ^to the undertaker, \\
      under^taker please drive ^slow, \\
      for this lady you are ^carrying, \\
      Lord I ^hate to ^see her ^go. \\
    \end{verse}
  
    \begin{chorus}[after-label=]\end{chorus}

    \columnbreak
    
    \begin{verse} 
      Oh, I ^followed close behind her, \\
      tried to ^hold up and be ^brave. \\
      But I could not hide my ^sorrow, \\
      when they ^laid her ^in the ^grave. \\
    \end{verse}

    \begin{chorus}[after-label=]\end{chorus}

    \begin{verse}
      I went ^back home, the home was \\ lonesome, \\
      since my ^mother, she was ^gone. \\
      All my brothers and sisters ^crying, \\
      what a ^home so ^sad and a^lone. \\
    \end{verse}
  
    \begin{chorus}[after-label=]\end{chorus}

    \begin{verse}
      We sang ^songs of childhood, \\
      hymns of ^faith that made us ^strong. \\
      Ones that mother maybelle ^taught us, \\
      hear the ^angels ^sing a^long. \\
    \end{verse}
  
    \begin{chorus}[after-label=]\end{chorus}

  \end{multicols}
\end{song}
\end{document}




  


 